{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
\section{Introduction}
    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ stronlyg convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.

    \par 
    A good choice of a minimization algorithm is the Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983}. 
    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
    \begin{align}
        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
        \\
        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
        \\
        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
        \\
        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
    \end{align}\label{eqn:example_algorithm}
    It's well known that if the minimizer $x^*$ exists, $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
    When $F$ is $\mu > 0$ strongly convex, the algorithm oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
    \par
    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it $\mathcal O(1/k^2)$ convergence rate is kept, and it performs empirically better. 
    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
    \par
    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_t)_{t \ge 1}$. 
    It also has descriptive power to describe several variants of FISTA in the literatures.

    \subsection{Contributions}
        Our contributions are two folds, theoretical and practical. 
        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
        The choices for $\theta_k$ varies for different varints of the accelerated proximal gradient algorithm. 
        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergencec rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$. 
        V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
        \par
        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
        \begin{align*}
            \mathcal O\left(
                \left(
                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                \right)
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right). 
        \end{align*}
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate. 
        And when $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}, which is an optimal algorithm for a strongly convex $F$. 
        R-WAPG gives the a convergence claim, and it's consistent with the literatures. 
        \par
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
    \subsection{Prior works}

    \subsection{Organizations}

@@

    Throughout, we assume the problem of types $F = f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
    We consider optimization problem: $\min_x \left\lbrace F(x) \defeq f(x) + g(x)\right\rbrace$.
    Fix arbitrary $y \in \RR^n$, define

@@

        (x; y) \defeq

@@

        \mathcal M^{L^{-1}}(x; y) := F(x) + \frac{L}{2}\Vert x - y\Vert^2, 
    and the proximal gradient operator $T_L = [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
    Define the Bregman divergence of $f$: 

@@

        Fix any $y$, we will have for all $x \in \RR^n$ that: 

@@

        Fix any $y$, we have for all $x$: 

@@

        Observe that the function $\widetilde {\mathcal M}(\cdot; x)$ is $L$ strongly convex with minimizer $T_Ly$. 
        For all $x \in \RR^n$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 

@@

        The content of the entire LHS of the conclusion of the claim is conclused in (3.2*). 

@@

                F(x_1) - F(x^*) + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2

@@

\section{Equivalent representations of R-WAPG}
    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
    In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
    This section carries out the tedious but necessary works for demonstrating the descriptive power of R-WAPG. 
    We will formulate it into three generic forms that are commonly seemed in the literatures. 
    These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
    \par 
    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} and finds a representation without using auxiliary sequence $\gamma_k, \hat \gamma_k$. 
    Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:r-wapg-momentum-repr} demonstrates two more equivalent representations of the R-WAPG intermediate form (Definition \ref{def:r-wapg-intermediate}) which are formulated into Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}. 
    Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
    In brief, the relations of these Propositions and Definitions can be summarized by
    \begin{align*}
        & \text{Definition } \ref{def:wapg} 
        \\
        & \iff 
        \text{Definition } \ref{def:r-wapg-intermediate} & \text{By Proposition }\ref{prop:wapg-first-equivalent-repr}
        \\
        & \iff \text{Definition }\ref{def:r-wapg-st-form} & \text{By Proposition }\ref{def:r-wapg-st-form} 
        \\
        & \;\implies 
        \text{Definition }\ref{def:r-wapg-momentum-form}. 
        & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}
    \end{align*}

@@

\section{R-WAPG describes existing accelerations scheme in the literatures}
    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are descriptive. 
    They generalize many existing sequences used in accelerated proximal gradient schemes. 
    \par
    This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
    \begin{lemma}[R-WAPG sequences as Inverted FISTA sequence]
        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
        If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
        \begin{enumerate}
            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$. 
        \end{enumerate}
    \end{lemma}
    \begin{proof}
        We start proving (i). 
        For all $k \ge 1$: 
        \begin{align*}
            \alpha_{k + 1}^2 
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 + (\mu/L) \alpha_k
            \\
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 
            \\
            \implies 
            \alpha_{k + 1}^2 
            & \ge (1 - \alpha_{k + 1})\alpha_k^2 
            &  \rho_k \ge 1
            \\
            \iff 
            \alpha_k^{-1} 
            &\ge 
            \alpha_{k + 1}^{-2} + \alpha_{k + 1}^{-1}. 
        \end{align*}
        When $k = 0$, it has $\alpha_0 = 1$. 
        By definition of $\rho_0$ we have 
        \begin{align*}
            \alpha_1^2 &= 
            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 
        \end{align*}
        Therefore (i) holds. 
        (i) is proved. 
        \par
        (i) $\implies$ (ii) because substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
        Solving the equality yields $t_{k + 1} = (1/2)\left(1 \pm \sqrt{1 + 4 t_k^2}\right)$ for all $k \ge 0$. 
        Since $\alpha_k \in (0, 1)$, it means $t_k > 0$, hence the valid root is the larger root which gives the upper bound for $t_{k + 1}$ so: 
        \begin{align*}
            t_{k + 1} \in \left(
                0, \frac{1}{2}\left(1 + \sqrt{1 + 4t_k^2}\right) 
            \right]
        \end{align*}
        To prove (iii), because $\rho_k \ge 1$, we have $\prod_{i = 1}^{k} \max(1, \rho_{k - 1})(1 - 
        \alpha_k)$ for all $k \ge 1 = \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$. 
        By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$: 
        \begin{align*}
            \alpha_k^2 &= \rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2
            \\
            \iff 
            \alpha_k^2/\alpha_{k - 1}^2 &= \rho_{k - 1}(1 - \alpha_k)
            \\
            \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)
            &= 
            \prod_{i = 1}^{k}\alpha_k^2 /\alpha_{k - 1}^2= \alpha_k^2/\alpha_0. 
        \end{align*}
        Because $\alpha_0 = 1$, (iii) is justified.

>>>>

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
\section{Introduction}
    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.

    \par 
    A good choice of a minimization algorithm is the Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983}. 
    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
    \begin{align}
        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
        \\
        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
        \\
        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
        \\
        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
    \end{align}\label{eqn:example_algorithm}
    It's well known that if the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
    When $F$ is $\mu > 0$ strongly convex, the algorithm oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
    \par
    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it $\mathcal O(1/k^2)$ convergence rate is kept, and it performs empirically better. 
    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
    \par
    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_t)_{t \ge 1}$. 
    It also has descriptive power to describe several variants of FISTA in the literatures.

    \subsection{Contributions}
        Our contributions are two folds, theoretical and practical. 
        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
        The choices for $\theta_k$ varies for different varints of the accelerated proximal gradient algorithm. 
        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergencec rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$. 
        V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
        \par
        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
        \begin{align*}
            \mathcal O\left(
                \left(
                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                \right)
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right). 
        \end{align*}
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate. 
        And when $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}, which is an optimal algorithm for a strongly convex $F$. 
        R-WAPG gives the convergence claim, and it's consistent with the literatures. 
        \par
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
    \subsection{Prior works}
        \todoinline{The following are notes to the writer. There is in fact little prior works in this regard. People tried to unify all the variants but all of them are trying to unify the convergence claims under one theorem. Flexible choices of the momentum parameters are the prime focus in heavy ball momentum, or FISTA with Hessian Damping. Their approaches are usually using dynamical system. }

    \subsection{Organizations}
        \todoinline{This will be written once most of the contents in the paper are settled. }

@@

    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
    We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$.
    Fix any arbitrary $y \in \RR^n$, define for all $x \in Q$: 

@@

        (x; y) 
        &:=

@@

        \mathcal M^{L^{-1}}(x; y) &:= F(x) + \frac{L}{2}\Vert x - y\Vert^2, 
    and the proximal gradient operator $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
    The proximal gradient operator $T_L$ admits 
        T_Ly = \argmin_x \left\lbrace
            g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
        \right\rbrace. 
    It is a single valued mapping and it has its domain on the entire $\RR^n$. 
    Another operator often associated with $T_L$ is the gradient mapping operator $\mathcal G_L:= L(I - T_L)$. 
    Finally, define the Bregman divergence of $f$: 

@@

        Fix any $y \in \RR^n$, we will have for all $x \in Q$ that: 

@@

        Fix any $y\in \RR^n$, we have for all $x \in Q$: 

@@

        Observe that the function $\widetilde {\mathcal M}(\cdot; y)$ is $L$ strongly convex with minimizer $T_Ly$. 
        For all $x \in Q$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 

@@

        The content of the entire LHS of the inequality we want to prove is in (3.2*). 

@@

                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2

@@

\section{Equivalent representations of R-WAPG}
    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
    In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
    This section carries out the tedious but necessary works for demonstrating the descriptive power of R-WAPG. 
    We will formulate it into three generic forms that are commonly seemed in the literatures. 
    These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
    \par 
    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} and finds a representation without using auxiliary sequence $\gamma_k, \hat \gamma_k$. 
    Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:r-wapg-momentum-repr} demonstrates two more equivalent representations of the R-WAPG intermediate form (Definition \ref{def:r-wapg-intermediate}) which are formulated into Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}. 
    Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
    In brief, the relations of these proposition and definitions can be summarized by
    \begin{align*}
        & \text{Definition } \ref{def:wapg} 
        \\
        & \iff 
        \text{Definition } \ref{def:r-wapg-intermediate} & \text{By Proposition }\ref{prop:wapg-first-equivalent-repr}.
        \\
        & \iff \text{Definition }\ref{def:r-wapg-st-form} & \text{By Proposition }\ref{def:r-wapg-st-form}.
        \\
        & \;\implies 
        \text{Definition }\ref{def:r-wapg-momentum-form}. 
        & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}.
    \end{align*}

@@

\section{R-WAPG describes existing accelerations scheme in the literatures}
    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are descriptive. 
    They generalize many existing sequences used in accelerated proximal gradient schemes. 
    \par
    This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
    \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
        If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
        \begin{enumerate}
            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$. 
        \end{enumerate}
    \end{lemma}
    \begin{proof}
        We start proving (i). 
        For all $k \ge 1$: 
        \begin{align*}
            \alpha_{k + 1}^2 
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 + (\mu/L) \alpha_k
            \\
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 
            \\
            \implies 
            \alpha_{k + 1}^2 
            & \ge (1 - \alpha_{k + 1})\alpha_k^2 
            &  \rho_k \ge 1
            \\
            \iff 
            \alpha_k^{-1} 
            &\ge 
            \alpha_{k + 1}^{-2} + \alpha_{k + 1}^{-1}. 
        \end{align*}
        When $k = 0$, it has $\alpha_0 = 1$. 
        By definition of $\rho_0$ we have 
        \begin{align*}
            \alpha_1^2 &= 
            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 
        \end{align*}
        Therefore (i) holds. 
        (i) is proved. 
        \par
        (i) $\implies$ (ii) because substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
        Solving the equality yields $t_{k + 1} = (1/2)\left(1 \pm \sqrt{1 + 4 t_k^2}\right)$ for all $k \ge 0$. 
        Since $\alpha_k \in (0, 1)$, it means $t_k > 0$, hence the valid root is the larger root which gives the upper bound for $t_{k + 1}$ so: 
        \begin{align*}
            t_{k + 1} \in \left(
                0, \frac{1}{2}\left(1 + \sqrt{1 + 4t_k^2}\right) 
            \right]
        \end{align*}
        To prove (iii), because $\rho_k \ge 1$, we have $\prod_{i = 1}^{k} \max(1, \rho_{k - 1})(1 - 
        \alpha_k)$ for all $k \ge 1 = \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$. 
        By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$: 
        \begin{align*}
            \alpha_k^2 &= \rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2
            \\
            \iff 
            \alpha_k^2/\alpha_{k - 1}^2 &= \rho_{k - 1}(1 - \alpha_k)
            \\
            \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)
            &= 
            \prod_{i = 1}^{k}\alpha_k^2 /\alpha_{k - 1}^2= \alpha_k^2/\alpha_0. 
        \end{align*}
        Because $\alpha_0 = 1$, (iii) is justified. 
    \end{proof}
    \begin{remark}
        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chmabolle, Dossal \cite{chambolle_convergence_2015}. 
    \end{remark}

    \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and they are constant meaning that there exists $\rho, \alpha$ such that $\alpha_k = \alpha$ and $\rho_k = \rho$ for all $k \ge 0$.
        Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
        Then the constant R-WAPG sequence satisfies: 
        \begin{enumerate}
            \item $\rho = (1 - \mu/L\alpha^{-1})/(1 - \alpha)$. 
            \item $\theta = (1 - \mu/L)(1 - \alpha)/(-\mu/L \alpha + 2\alpha - \alpha^2)$. 
            \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = (1 - \sqrt{\mu/L})/(1 + \sqrt{\mu/L})$. 
        \end{enumerate}
    \end{lemma}

    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\;\\
        Fix arbitrary $a \ge 2$.
        Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
            \alpha_k &= a/(k + a), 
            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)}. 
        Consider the algorithm given by: 
            Initialize any $y_1 = x_1$. 
            For $k = 1, 2, \cdots$, update: 
                & x_{k + 1} := y_k + L^{-1}\mathcal G_L(y_k), 
                & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
                & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
        If $\mu = 0$, then $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid pair of R-WAPG sequence from Definition \ref{def:rwapg-seq} and the above algorithm is a valid form of R-WAPG. 
        Assume minimizer $x^*$ exists for function $F$. 
        Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(1/k^2)$. 
        We only need to show that $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are valid R-WAPG sequences. 
        To do that we verify equality $\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k \alpha_k^2$ because it's assumed $\mu = 0$ in this case. 
        For all $k \ge 0$, the right side of the equality evaluates to 
            \alpha_k^2 \rho_k(1 - \alpha_{k + 1}) &= 
                \frac{\alpha}{k + 1}
            \right)^2 \left(
                \frac{(k + a)^2}{(k + 1)(k + a + 1)}
                1 - \frac{a}{k + 1 + a}
            &= \left(
                \frac{\alpha}{k + 1}
            \right)^2 \left(
                \frac{(k + a)^2}{(k + 1)(k + a + 1)}
                \frac{k + 1}{k + 1 + a}
            &= \frac{a^2}{(k + a + 1)^2} = \alpha_{k + 1}^2. 
        Therefore, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ is a pair of valid R-WAPG sequence. 
        So, it can be used in the R-WAPG algorithm and represent it in R-WAPG Momentum Form in Definition \ref{def:r-wapg-momentum-form}. 
        Using $\mu = 0$, it simplifies the momentum term in Definition \ref{def:r-wapg-momentum-form} and gives the rules of updates in the theorem statement. 
        Next, we show the convergence rate of the algorithm. 
        Observe that $(\forall k \ge 0)(\forall a \ge 2)$, $\rho_k$ has 
            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)} 
            &> \frac{(k + 1)^2}{(k + 1)(k + a + 1)} 
            & \text{By } a \ge 2. 
            &= \frac{(k + 1)}{(k + a + 1)} 
            & > 1.   & \text{By } a > 2. 
        Hence (iii) in Lemma \ref{lemma:inverted-fista-seq} applies. 
        We may use Proposition \ref{prop:wagp-convergence} by the validity of our $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ sequences, we have:
            & F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            & = F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert x_{k + 1} - x^* + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
            & \le 
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \alpha_k^2
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            & \text{By Lemma \ref{lemma:inverted-fista-seq} (iii). }
            \left(\frac{a}{k + a}\right)^2
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
        We can replace $v_1$ to be $x_1$ by Proposition \ref{prop:r-wapg-momentum-repr}. 
